---
title: "XiaolanWan"
author: "Xiaolan"
date: "1/27/2022"
output: html_document
---

## Building a book
Deliverable (1): the last word in Chapter 15 is class.

Deliverable (2): as I tried to build the book, I encoutered the following error:

Quitting from lines 4-5 (Introduction.Rmd) 
Error in dev.control(displaylist = if (record) "enable" else "inhibit") : 
  dev.control() called without an open graphics device
Calls: local ... call_block -> block_exec -> eng_r -> chunk_device -> dev.control
In addition: Warning messages:
1: In grSoftVersion() :
  unable to load shared object '/Library/Frameworks/R.framework/Resources/modules//R_X11.so':
  dlopen(/Library/Frameworks/R.framework/Resources/modules//R_X11.so, 6): Library not loaded: /opt/X11/lib/libSM.6.dylib
  Referenced from: /Library/Frameworks/R.framework/Versions/4.0/Resources/modules/R_X11.so
  Reason: image not found
2: In cairoVersion() :
  unable to load shared object '/Library/Frameworks/R.framework/Resources/library/grDevices/libs//cairo.so':
  dlopen(/Library/Frameworks/R.framework/Resources/library/grDevices/libs//cairo.so, 6): Library not loaded: /opt/X11/lib/libXrender.1.dylib
  Referenced from: /Library/Frameworks/R.framework/Versions/4.0/Resources/library/grDevices/libs/cairo.so
  Reason: image not found
3: In (function (filename = if (onefile) "Rplots.pdf" else "Rplot%03d.pdf",  :
  failed to load cairo DLL
Execution halted
Error in Rscript_render(f, render_args, render_meta, add1, add2) : 
  Failed to compile Introduction.Rmd
Calls: local ... <Anonymous> -> render_new_session -> Rscript_render
Execution halted
Error: bookdown::render_book() failed to render the output format 'bookdown::pdf_book'.
Execution halted

Exited with status 1.

I read the warning message carefully, which told me that "Library not loaded: /opt/X11/lib/libSM.6.dylib", then I googled how to library X11 and I was told to install a software called "XQuartz", which can allow me to use run X11. After I installed this software, this issue was solved. 

## US weather station
```{r}
library(tidyverse)
weather <- readr::read_fwf("~/Desktop/2021 Fall/585/lab1_xiaolan/ushcn-v2.5-stations.txt",
         fwf_positions(c(1, 3, 4, 6, 13, 22, 33, 39, 42, 73, 80, 87, 94),
                       c(2, 3, 5, 11, 20, 30, 37, 40, 71, 78, 85, 92, 95),
                       c("COUNTRY CODE", "NETWORK CODE", "ID PLACEHOLDERS",
                         "COOP ID", "LATITUDE",  "LONGITUDE",
                         "ELEVATION",  "STATE", "NAME",
                         "COMPONENT 1", "COMPONENT 2", "COMPONENT 3", "UTC OFFSET")
                       ))
weather$ELEVATION <- weather$ELEVATION %>% as.numeric()
```


```{r}

library(maps)
states_map <- map_data("state")
weather$zone <- as.character(weather$`UTC OFFSET`)

ggplot(data = weather,
       aes(x = LONGITUDE, y = LATITUDE,
           color = ELEVATION))+
  geom_map(data = states_map, map = states_map,
                   aes(x = long, y = lat, map_id = region),
                   color = "black", fill = "white", size = 0.3) +
  geom_point(aes(shape = zone))  +
  scale_color_gradient(low = "green", high = "red", na.value = NA)
```

